NEXTY: A CONSENSUS TO GET ZERO TRANSFER FEE AND INSTANT TRANSFER BLOCKCHAIN

### 2018-06-18 Paper.tex
Fix typo and update to nexty.io email

\title{NEXTY: A CONSENSUS TO GET ZERO TRANSFER FEE AND INSTANT TRANSFER BLOCKCHAIN}
\author{
	Thanh Dao \& Ha Dang \\
	Co-founder/CTO @ Nexty Platform \\
	thanhdao@nexty.io / dvietha@gmail.com
}
\date{} % delete this line to display the current date

@@

Total reward $\Re$ is the amount of {\small NTF} was produced after each sealing round, calculated as \textit{[reward generated in one block]} * \textit{[number of blocks generated in that sealing round]}.

>>>>

\title{NEXTY: A CONSENSUS TO GET ZERO TRANSFER FEE AND INSTANT TRANSFER BLOCKCHAIN}
\author{
	Thanh Dao \& Ha Dang \\
	Co-founder/CTO @ Nexty Platform \\
	thanhdao@nexty.io / hadang@nexty.io
}
\date{} % delete this line to display the current date

@@

Total reward $\Omega$ is the amount of {\small NTF} was produced after each sealing round, calculated as \textit{[reward generated in one block]} * \textit{[number of blocks generated in that sealing round]}.
